Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-11 cvpr2018.tex
experiment

\subsection{Training Details}
%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
The Adam optimizer is used for all experiments.  The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO). The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).
For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
We use 1-repeat residual block for the generator till $256^2$ resolution.
To generate $512^2$ images, we pre-train the generator to $256^2$ for the consideration of memory saving and faster convergence. We use $3$-repeat res-block followed by the stretching and linear compression layer. Since the $256^2$ image already decides the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.

@@

\textbf{Dataset} 
\textcolor{red}{We evaluate our method extensively using three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. We pre-process and split the images using the same pipeline in \cite{reed2016generative,han2017stackgan}
%, which crops the bird region and ensure the foreground occupies greater than 0.75.  
The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
%We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
Each image in both datasets is associated with 10 text descriptions. \textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.  Each image has 5 text descriptions.  }
We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description of the three datasets into a 1024 vector.
%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
}

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model pre-trained on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.

\textbf{Visual-semantic similarity~}
Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description. We introduce a new qualitative measurement, namely neural visual-semantic similarity (VS similarity) \cite{vsemb}. Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map the image and sentence embeddings into one semantic space, using the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.

@@

@@

Ideally, a trained model should learn a smooth linear latent manifold of the images. To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences. During this experiment, we fix the all the random noises to make the object and background consistent. As is shown in Figure~\ref{}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape. In the first row, the generated birds gradually turn the color from red to yellow, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.

We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
						&	 CUB		&	Oxford  & COCO		     \\ \hline
			StackGAN     &	$0.228{\pm}.162$	&	 $0.278{\pm}.134$			&  $-{\pm}-$		\\

			Ground Truth	&	${0.302{\pm}.151}$	&	$ {0.336{\pm}.138}$			&  -  \\ \hline
			HDGAN 		&	$\bm{0.259{\pm}.159}$	&	$ \bm{-{\pm}-}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The visual-semantic similarity evaluation on three datasets. The higher score represents higher degree of matching between the generated images and the text information. } \label{table:score}
\end{table}

@@

\subsection{On the Local Image Loss}
\begin{table}[t] % retrieval
	\label{tab:local_loss}
	\begin{center}
		\begin{tabularx}{.36\textwidth}{c|cc}
			\specialrule{1.5pt}{0pt}{0pt}  
			Metric 					&   No Local 	       &    With Local	\\  \hline
			MS-SSMI                 &   $-$                &	$0.215$ \\  \hline
			VS similarity           &   $-$                &	$0.259{\pm}.159$ \\ \hline
			Inception score         &   $-$   &  	$4.15{\pm}.05$ \\
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
\end{table}

We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64 and 256 $\times$ 256. 
As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}. To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, also both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more details, thus improving the visual quality.

@@

\section{Conclusion}
...

{\small
\bibliographystyle{ieee}
\bibliography{reference_zizhao,egbib}
}

>>>>

\subsection{Training Details}
%The algorithm that summarizes the training process of our model is given in Algorithm 1. 
%We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4.
The Adam optimizer is used for all experiments.  The initial learning rate is set as 0.0002 and decreased by half for every 100 epochs (30 for COCO). The CUB and Oxford-102 datasets are trained for 500 epochs in total (250 epochs for COCO with 4 GPUs).\textcolor{red}{flower is actually 580, maybe does not matter.}
For the adaptive local image loss, we set $R=1$ for $64^2$ side output, $R=3$ for $128^2$ side output and $R=5$ for $256^2$ and $512^2$ outputs.
We use 1-repeat residual block for the generator till $256^2$ resolution.
To generate $512^2$ images, we pre-train the generator to $256^2$ due to the limitation of GPU memory. We use $3$-repeat res-block followed by the stretching and linear compression layer. \textcolor{red}{maybe delete the l1 loss description}
%Since the $256^2$ image already captures the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.
%for the consideration of memory saving and faster convergence.

@@

\textbf{Dataset} 
\textcolor{red}{We evaluate our method extensively using three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. We pre-process and split the images following the same pipeline in \cite{reed2016generative,han2017stackgan}
%, which crops the bird region and ensure the foreground occupies greater than 0.75.  
The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
%We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
Each image in both datasets is associated with 10 text descriptions. \textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.  Each image has 5 text descriptions. }
We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description  into a 1024 embedding vector.
%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
}

\textbf{Evaluation metric}
We use three different quantitative metrics to evaluate our method.
%\textcolor{red}{\textbf{Inception score.}}  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
% \begin{equation}
%	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
% \end{equation}
% where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}. 
1) Inception score \cite{improvedGAN} is a measurement of both objectiveness and diversity of generated images, it is closely correlated with human judgment on the image quality. For CUB and oxford-102, we use the fine-tuned inception model provided by StackGAN. For MS COCO dataset, we directly use the model pre-trained on ImageNet.
2) We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance. 3) Visual-semantic similarity.

\textbf{Visual-semantic similarity~}
Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) \cite{vsemb}. Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.

@@

Table \ref{table:vss} shows the qualitative vs-similarity comparison results on three datasets. We also add the evaluation results on the ground truth image and sentence pair for reference. Our proposed method achieves much better results on both CUB and Oxford datasets. Since we do not have a pre-trained  StackGAN model for coco dataset, we omit the comparison. This results demonstrate that HDGAN is better at capturing visual semantic correlation.

@@

Ideally, a trained model should learn a smooth linear latent manifold of the images. To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences. During this experiment, we fix the all the random noises to make the object and background consistent. As is shown in Figure~\ref{}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape. In the first row, the generated birds gradually turn the color from yellow to red, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.

\textcolor{red}{We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.}

\begin{table}[t] % retrieval
	\label{table:vss}
	\begin{center}
		\begin{tabularx}{.477\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
						&	 CUB		&	Oxford  & COCO		     \\ \hline
			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\

			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
		\end{tabularx} \vspace{-.4cm}
	\end{center}
	\caption{The visual-semantic similarity evaluation on three datasets. The higher score represents higher degree of matching between the generated images and the text information. } 
\end{table}

@@

\subsection{On the Local Image Loss}
\begin{table}[t] % retrieval
	\label{tab:local_loss}
	\begin{center}
		\begin{tabularx}{.43\textwidth}{c|ccc}
			\specialrule{1.1pt}{0pt}{0pt}  
			Metric 			 		&   wo/Img 	 & w/global     &   w/local	\\  \hline
			MS-SSMI                 &   $-$      &   $-$           &	$.215$ \\  \hline
			VS similarity           &   $-$      &   $-$           &	$.246{\pm}.157$ \\ \hline
			Inception score         &   $-$ 	 &   $-$		   &    $4.15{\pm}.05$ \\
		\end{tabularx}
	\end{center} \vspace{-.4cm}
	\caption{Results using three quantitative evaluation metrics on birds dataset.} \label{table:imgloss}
\end{table}

We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset. 
As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}. To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality.

@@

\section{Conclusion}
In this paper, we present a novel and effective method to tackle the problem of generating high resolution images using text description. We introduce the hierarchical nested side outputs for deeply supervising the GAN training. To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to boost the training. We also introduce a newly evaluation method for conditional gan, which leverage visual semantic embedding to judge the matching between generated images and provided text description, thus remove the necessary for human evaluation.
Extensive experiment results demonstrate that our method work significantly better than existing state of the arts.
{\small
\bibliographystyle{ieee}
\bibliography{reference_zizhao,egbib}
}
